Routines and Regret: An Examination of Behavioral Norms and Emotional Responses

### 2024-02-15 paper/paper.qmd
done

## Implications of Regret Research
Research on regret is important because regret is prevalent in life. First, understanding how regret works can help in designing therapeutic interventions that more effectively manage regret, depression, and anxiety. For example, in the car accident incident in part2, Mr. Adams in the exception scenario would have developed greater regret and had a greater likelihood of developing psychological problems than Mr. White. One can intervene and treat Mr. Adams more proactively by gaining insight into regret. Second, insights into regret can provide strategies for improving decision-making processes in personal, professional, and political contexts, emphasizing the importance of normative behaviors and their impact on outcomes.

@@

@@

Weaknesses and next steps should also be included.

@@

# Save the cleaned data
write_csv(
  x = data,
  file = here::here("data/analysis_data/exp1-labeled-data.csv")
)
```
```

>>>>

@@

Research on regret is important because regret is prevalent in life. First, understanding how regret works can help in designing therapeutic interventions that more effectively manage regret, depression, and anxiety. For example, in the car accident incident in part2, Mr. Adams in the exception scenario would have developed greater regret and had a greater likelihood of developing psychological problems than Mr. White. One can intervene and treat Mr. Adams more proactively by gaining insight into regret. Second, insights into regret can provide strategies for improving decision-making processes in personal, professional, and political contexts, emphasizing the importance of normative behaviors and their impact on outcomes.

@@

@@

write_csv(
  x = data,
  file = here::here("data/analysis_data/exp1-labeled-data.csv")
)
```
